---
title: 'Differential Connectivity Analysis Report'
date: 'Report Created: `r Sys.Date()`'
output:
  html_document:
    theme: simplex
    toc: false
    df_print: paged
---


# Parameters
**Covariate**: `r output$args$covariate`  
**Reference Group**: `r output$args$ctrl`  
**Test Group**: `r output$args$cond`  
**Simulation Type**: `r output$args$sim_type`  
**Iterations**: `r output$args$iter`  
**Cores**: `r output$args$cores`  
**Mean Background Correction**: `r output$args$mean_correct`  
**Differential Connectivity Type**: `r output$args$mdc_type`  
**Plotting**: `r output$args$plotting`  
**Report Directory**: `r output$args$report_path`  

***

# Background Statistics
**`r output$args$ctrl` Background**: `r output$bg$mc_r_bg`  
**`r output$args$cond` Background**: `r output$bg$mc_t_bg`  

***


```{r setup, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
library(kableExtra)
options(scipen=1, digits=3)
```


# Results
```{r}
mdc
```


# Visualizations
##  {.tabset .tabset-fade}
  

### P1 
```{r P1, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P1']]
p2 <- output$plots$permutations[['P1']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```


### P2 
```{r P2, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P2']]
p2 <- output$plots$permutations[['P2']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```


### P3 
```{r P3, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P3']]
p2 <- output$plots$permutations[['P3']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```


### P4 
```{r P4, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P4']]
p2 <- output$plots$permutations[['P4']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```


### P5 
```{r P5, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P5']]
p2 <- output$plots$permutations[['P5']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```


### P6 
```{r P6, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P6']]
p2 <- output$plots$permutations[['P6']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```


### P7 
```{r P7, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P7']]
p2 <- output$plots$permutations[['P7']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```


### P8 
```{r P8, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P8']]
p2 <- output$plots$permutations[['P8']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```


### P9 
```{r P9, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P9']]
p2 <- output$plots$permutations[['P9']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```


### P10 
```{r P10, fig.width=9, fig.align='center'}
p1 <- output$plots$connectivity[['P10']]
p2 <- output$plots$permutations[['P10']]
ggarrange(p1, p2, ncol=2, widths=c(0.4, 0.6))
```

